---
title: "About"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(PubMedWordcloud)
library(magrittr)
author <- "nakken s"
pmid <- getPMIDs(author = author, dFrom = 2007, dTo = 2020, n = 200)
pmid <- c(31209238,pmid)
pmid <- pmid[pmid != "23054375"]
abstracts <- getAbstracts(pmid)

words <- cleanAbstracts(abstracts) %>%
  dplyr::mutate(word = stringr::str_trim(word))

words <- dplyr::filter(words, !stringr::str_detect(word,"^(well|will|interpret|data|using|detect|target|function|large|also|show|recent|different|low|likely|information|number|peer|iih|last|indicate|tested|context|series|studies|observ|across|novel|potential|character|negative|acessi|related|estimate|sample|provide|explain|without|interval|region|point|analys|analyz|present|findings|includ|subseq|respectiv|selecte|unknown|cases|impact|method|use|sites|used|result|avail|first|one|study|multiple|however|predict|despite|identifi|associa|within|found|perform|comprehens|develop|review|affect|finnish|whether|since|can|two|cell|previous|risks|previously|prospectively|time|crude|p|cause|caused|limited|among|followed|significantly|identified|observed|including|developed|compared|available|performed|significant|combinations|lines|provide|high|related|potential|thus|new|particular|controls|compare|years|age|may|set|accessi|addition|lower|analyzed|interpretation|results|lower|higher|reported|methods|predicted|detected|associated|cancers|comprehensive|patient|included|authors|affecting|respectively|gene|variant|subsequent|stage)$"))
words <- head(words,100) %>%
  dplyr::mutate(word = stringr::str_replace_all(word,"^brca$|brca$","BRCA")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"^crc$","CRC")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"^atm$","ATM")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"^braf$","BRAF")) %>%
  dplyr::mutate(word = stringr::str_replace_all(word,"^mlh$|mlh$","MLH")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"abcb","ABCB")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"vus","VUS")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"snps","SNPs")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"fto","FTO")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"tle","TLE")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"rna","RNA")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"check","CHEK")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"^mmr$|mmr$","MMR")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"^msh$|msh$","MSH")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"^aqp$|aqp$","AQP")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"^kcnj$|kcnj$","KCNJ")) %>%
  dplyr::mutate(word = stringr::str_replace_all(word,"^path","path_")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"path_ogenic","pathogenic")) %>%
  dplyr::mutate(word = stringr::str_replace(word,"^dna$","DNA"))

```

<p>I am a research scientist working in [Eivind Hovig's group](http://radium.no/hovig) at the [Institute for Cancer Research](http://radium.no) in Oslo, Norway. Most of my activities involve cancer data science, i.e. analysis of data from high-throughput molecular profiling of tumor samples. During the last years, I have been part of the [Norwegian Cancer Genomics Consortium](http://cancergenomics.no), a national effort on clinical cancer genomics. I am currently affiliated with the [Centre for Cancer Cell Reprogramming (CanCell)](http://www.med.uio.no/cancell/english/). My background is in computer science from [NTNU](http://www.ntnu.no)/[University of Minnesota](http://www.umn.edu), and I received my [PhD in computational biology](/thesis/PhD_Thesis_SigveNakken.pdf) from the [Centre for Molecular Biology and Neuroscience](http://www.cmbn.no) at the [University of Oslo](http://www.uio.no).</p>

<p>Main ongoing research activities:

   * _Cancer genome interpretation_

   * _Computational modeling of drug response in cancer_

   * _Cancer predisposition_


I supervise MSc students at the [Department of Informatics, University of Oslo](https://www.mn.uio.no/ifi/), which have included projects on: 

* [text mining of clinical trial data](https://www.duo.uio.no/handle/10852/38306)
* [evaluation of methods for cancer driver gene prediction](https://www.duo.uio.no/handle/10852/41622)
* [cluster analysis of data from genome-wide association studies](https://www.duo.uio.no/handle/10852/53017)
* [comparison of somatic and germline mutational spectra](https://www.duo.uio.no/handle/10852/57756)

<br>
<p>
A wordcloud of papers I have co-authored:
</p>
```{r publication_word_cloud, echo = F}
plotWordCloud(words[], rot.per = 0, scale = c(5,0.3))
```
