---
title: "About"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(PubMedWordcloud)
author <- "nakken s"
pmid <- getPMIDs(author = author, dFrom = 2007, dTo = 2018, n = 200)
abstracts <- getAbstracts(pmid)
words <- cleanAbstracts(abstracts)

words <- dplyr::filter(words, word != 'developed' & word != 'high' & word != 'patient' & word != 'associated' & word != 'identified' & word != 'found' & word != 'performed' & word != 'potential' & word != 'including' & word != 'results' & word != 'developed' & word != 'available' & word != 'compared' & word != 'can' & word != 'may' & word != 'study' & word != 'associated' & word != 'one' & word != 'two' & word != 'first' & word != 'however' & word != 'used' & word != 'analyzed' & word != 'patients' & word != 'years' & word != 'present' & word != 'subsequent' & word != 'age' & word != 'whether' & word != 'use')
words400 <- words[1:400, ]

```

<p>I am a research scientist working in [Eivind Hovig's group](http://radium.no/hovig) at the [Institute for Cancer Research](http://radium.no) in Oslo, Norway. Most of my activities involve cancer data science, i.e. analysis of data from high-throughput molecular profiling of tumor samples. During the last years, I have been part of the [Norwegian Cancer Genomics Consortium](http://cancergenomics.no), a national effort on clinical cancer genomics. I am currently affiliated with the [Centre for Cancer Cell Reprogramming (CanCell)](http://www.med.uio.no/cancell/english/). My background is in computer science from [NTNU](http://www.ntnu.no)/[University of Minnesota](http://www.umn.edu), and I received my [PhD in computational biology](/thesis/PhD_Thesis_SigveNakken.pdf) from the [Centre for Molecular Biology and Neuroscience](http://www.cmbn.no) at the [University of Oslo](http://www.uio.no).</p>

<p>Main ongoing research activities:

   * _Cancer genome interpretation_

   * _Computational modeling of drug response in cancer_

   * _Cancer predisposition_


I supervise MSc students at the [Department of Informatics, University of Oslo](https://www.mn.uio.no/ifi/), which have included projects on: 

* [text mining of clinical trial data](https://www.duo.uio.no/handle/10852/38306)
* [evaluation of methods for cancer driver gene prediction](https://www.duo.uio.no/handle/10852/41622)
* [cluster analysis of data from genome-wide association studies](https://www.duo.uio.no/handle/10852/53017)
* [comparison of somatic and germline mutational spectra](https://www.duo.uio.no/handle/10852/57756)

<br>
<p>
A wordcloud of papers I have co-authored:
</p>
```{r publication_word_cloud, echo = F}
plotWordCloud(words400[], rot.per = 0, scale = c(5,0.3))
```
