---
title: "About"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(PubMedWordcloud)
author <- "nakken s"
pmid <- getPMIDs(author = author, dFrom = 2007, dTo = 2020, n = 200)
pmid <- c(31209238,pmid)
abstracts <- getAbstracts(pmid)
abstracts <- abstracts[-22]
words <- cleanAbstracts(abstracts)

words <- dplyr::filter(words, !stringr::str_detect(word,"^(well|will|interpret|data|using|detect|target|function|large|also|show|recent|different|low|likely|information|number|peer|iih|last|indicate|tested|context|series|studies|observ|across|novel|potential|character|negative|acessi|related|estimate|sample|provide|explain|without|interval|region|point|analys|analyz|present|findings|includ|subseq|respectiv|selecte|unknown|cases|impact|method|use|sites|used|result|avail|first|one|study|multiple|however|predict|despite|identifi|associa|within|found|perform|comprehens|develop|review|affect|provide|high|related|potential|thus|new|particular|controls|compare|years|age|may|set|accessi|addition)"))
words <- head(words,120)

```

<p>I am a research scientist working in [Eivind Hovig's group](http://radium.no/hovig) at the [Institute for Cancer Research](http://radium.no) in Oslo, Norway. Most of my activities involve cancer data science, i.e. analysis of data from high-throughput molecular profiling of tumor samples. During the last years, I have been part of the [Norwegian Cancer Genomics Consortium](http://cancergenomics.no), a national effort on clinical cancer genomics. I am currently affiliated with the [Centre for Cancer Cell Reprogramming (CanCell)](http://www.med.uio.no/cancell/english/). My background is in computer science from [NTNU](http://www.ntnu.no)/[University of Minnesota](http://www.umn.edu), and I received my [PhD in computational biology](/thesis/PhD_Thesis_SigveNakken.pdf) from the [Centre for Molecular Biology and Neuroscience](http://www.cmbn.no) at the [University of Oslo](http://www.uio.no).</p>

<p>Main ongoing research activities:

   * _Cancer genome interpretation_

   * _Computational modeling of drug response in cancer_

   * _Cancer predisposition_


I supervise MSc students at the [Department of Informatics, University of Oslo](https://www.mn.uio.no/ifi/), which have included projects on: 

* [text mining of clinical trial data](https://www.duo.uio.no/handle/10852/38306)
* [evaluation of methods for cancer driver gene prediction](https://www.duo.uio.no/handle/10852/41622)
* [cluster analysis of data from genome-wide association studies](https://www.duo.uio.no/handle/10852/53017)
* [comparison of somatic and germline mutational spectra](https://www.duo.uio.no/handle/10852/57756)

<br>
<p>
A wordcloud of papers I have co-authored:
</p>
```{r publication_word_cloud, echo = F}
plotWordCloud(words[], rot.per = 0, scale = c(5,0.3))
```
